\documentclass[letterpaper,11pt]{letter}

\usepackage[margin=1.0in]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagenumbering{gobble}
\usepackage{parskip}
\usepackage{hyperref}
\hypersetup{colorlinks,urlcolor=blue}
\newcommand{\ts}{\textsuperscript}
\longindentation=0pt

\signature{David Hanson}
\address{
    David Hanson \\ 
    4509 N Via Entrada, Apt. 154 \\
    Tucson, AZ 85718 \\
    (206) 293-9234 \\
    \href{mailto:davidhanson.c@gmail.com}{davidhanson.c@gmail.com} \\
}

\begin{document}
\begin{letter}{
    Hiring Manager \\
    Martin, White, \& Griffis \\
    3501 East Speedway Boulevard, Suite 225 \\
    Tucson, AZ  85716
}

\opening{Dear Hiring Manager,}

I have a passion for innovative projects and am keenly interested in working for your company. I recently moved to Tucson for my wife to start medical school, and I often admire the firm's work as I take her to the University of Arizona Health Sciences Innovation Building. The structural expertise exhibited convinces me that Martin, White, \& Griffis is somewhere I could develop and thrive as an engineer.

In 2016 I earned my Master of Science in Structural Engineering degree from the University of Washington, specializing in seismic analysis and design of steel and concrete structures. With almost 4 years of qualifying experience, I intend to obtain a California Professional Engineering license as soon as I am able.

% My primary engineering experience took place with Magnusson Klemencic Associates (MKA) where I designed high-rise residential and office buildings with a team of three to five highly skilled engineers. I received extensive in-house training, particularly in the design of concrete systems.

My primary engineering experience took place with Magnusson Klemencic Associates (MKA) where I worked with a team of three to five highly skilled engineers designing high-rise residential and office buildings such as One Chicago Square. I received extensive in-house training, particularly in the design of concrete systems.

A distinctive strength of mine beyond design and construction administration skills is that I excel as a team player. I have been able to connect with people from a broad range of personal and professional experience, and intentionally invest in developing strong, trusting relationships. I consistently seek feedback and constructive criticism as I believe it is through mutual support and learning from my peers that the team is built into a stronger unit and I also grow as an engineer. 

With my exceptional training from MKA and my team-oriented outlook, I am confident that given the opportunity I would become an asset to Martin, White, \& Griffis, a company with whom I would be proud to be associated. 

I would appreciate the opportunity to interview with you at your convenience and hope you will give my resume your favorable consideration. 

\closing{Sincerely,}

\end{letter}

\end{document}
% valuing integrity and fostering long standing relationships with people,

% I worked for Magnusson Klemencic Associates for almost two years before moving to Tucson designing high-rise residential and office buildings with a team of three to five highly skilled engineers. I received extensive in-house training, particularly in the design of concrete systems. I also became the primary engineering contact for the construction of a 32-story residential building in Austin, Texas, working directly with MKA Principal, Adam Theiss, to provide appropriate solutions for arising problems. My proficiency in analysis programs such as SAP, ETABS, and RAM Structural Systems complement my qualifications.
